### 2018-06-03 CS761-RandomizedAlgorithms/assignments/a1.tex
q6

\newpage
\section{}
\subsection{a}
\paragraph{}
\begin{align*}
M_{X^2}(t) &= E[e^{tX^2}] \\
&= \int_{-\infty}^\infty e^{tx^2}f(x)dx \\
&=\int_{-\infty}^\infty \frac{1}{\sqrt{2\pi}}e^{tx^2-\frac{1}{2}x^2}dx \\
&= \int_{-\infty}^\infty \frac{1}{\sqrt{2\pi}}e^{\frac{-1}{2}(1-2t)x^2}dx \\
&= \frac{1}{\sqrt{1-2t}}\int_{-\infty}^\infty \frac{1}{\sqrt{2\pi}}e^{z^2}dz &\text{Taking $z=\sqrt{1-2t}x$} \\
&= \frac{1}{\sqrt{1-2t}} &\text{Using $\int_{-\infty}^\infty f(x)dx = 1$}.
\end{align*}
\subsection{b}
\paragraph{}
Using Taylor expansion we have
\begin{align*}
E[X^4] = M_{X^2}^{(2)}(0).
\end{align*}
Now observe that
$$M_{X^2}^{(2)}(t) = \frac{3}{(1-2t)^{5/2}}$$
and so
$$M_{X^2}^{(2)}(0) = 3.$$
Therefore $E[X^4] = 3$.
\subsection{c}

\end{document}

>>>>

\newpage
\section{}
\subsection{a}
\paragraph{}
\begin{align*}
M_{X^2}(t) &= E[e^{tX^2}] \\
&= \int_{-\infty}^\infty e^{tx^2}f(x)dx \\
&=\int_{-\infty}^\infty \frac{1}{\sqrt{2\pi}}e^{tx^2-\frac{1}{2}x^2}dx \\
&= \int_{-\infty}^\infty \frac{1}{\sqrt{2\pi}}e^{\frac{-1}{2}(1-2t)x^2}dx \\
&= \frac{1}{\sqrt{1-2t}}\int_{-\infty}^\infty \frac{1}{\sqrt{2\pi}}e^{z^2}dz &\text{Taking $z=\sqrt{1-2t}x$} \\
&= \frac{1}{\sqrt{1-2t}} &\text{Using $\int_{-\infty}^\infty f(x)dx = 1$}.
\end{align*}
\subsection{b}
\paragraph{}
Using Taylor expansion we have
\begin{align*}
E[X^4] = M_{X^2}^{(2)}(0).
\end{align*}
Now observe that
$$M_{X^2}^{(2)}(t) = \frac{3}{(1-2t)^{5/2}}$$
and so
$$M_{X^2}^{(2)}(0) = 3.$$
Therefore $E[X^4] = 3$.
\subsection{c}
\paragraph{}
Let $t$ be a value to be chosen later. We have the following
\begin{align*}
Pr(Y > 1+\epsilon) &= Pr(e^{tY}> e^{t(1+\epsilon)} \\
&\leq E[e^{tY}]\cdot e^{-t(1+\epsilon)}  &\text{Using Markov's inequality} \\
&= (\Pi_{i=1}^k E[e^{\frac{t}{k}X_i^2}])e^{-t(1+\epsilon)} &\text{Using independence of $X_i^2$'s} \\
&=(\frac{1}{1-\frac{2}{k}t})^{\frac{k}{2}}e^{-t(1+\epsilon)} &\text{by $5a$}.
\end{align*}
Taking $t=\frac{k}{2}\frac{\epsilon}{1+\epsilon}$ we have
\begin{align*}
Pr(Y>1+\epsilon) &\leq (1 - \frac{\epsilon}{1+\epsilon})^\frac{-k}{2}e^{\frac{-k}{2}\epsilon}\\
&=e^{-\frac{k}{2}(\ln(1-\frac{\epsilon}{1+\epsilon}) + \epsilon)}
\end{align*}

\newpage
\section{}
\paragraph{}
We apply the following theorem from Lecture $4$ (here $H$ is the graph obtain by the uniform sampling algorithm):
\begin{theorem}
	Set $p=\frac{9\ln n}{\epsilon^2 c}$ where $c$ is the min-cut value of $G$. Then $H$ is a $(1\pm \epsilon)$-cut-approximator of $G$ with $O(p\cdot |E(G)|)$ edges with probability $1-\frac{4}{n}$.
\end{theorem}
We suppose that $G$ is a complete graph where each edge has the same weight, say $w$. In $G$ the value of a cut $\delta(S)$ is
$$w|\delta(S)| = w|S|(n-|S|)$$
and this function is minimized when $|S| = 1$, i.e. $S$ is a singleton. Therefore the minimum value of a cut in $G$ is $c = w(n-1)$. Therefore applying the above theorem we have
$$|E(H)| \leq O(p|E(G)|) = O(\frac{9\ln n}{\epsilon^2 w (n-1)}n(n-1)) \leq O(\frac{n\ln n}{\epsilon^2})$$
as desired.
\paragraph{Part 2}
Now we consider an unweighted complete graph $G$. Suppose for a contradiction the uniform sampling algorithm can obtain a  $(1\pm \epsilon)$-cut-approximator $H$ of $G$ with $o(n\ln n)$ edges. To achieve this our sampling probability $p$ can be at most $\frac{\ln n}{c n}$ for some constant $c>1$. Heuristically, lets take
$$p= \frac{\ln n}{100 n}.$$
Now let $v \in V(G)$. Then the probability that the degree of $v$ in $H$ is $0$ is
$$Pr(d_H(v) = 0) = (1- \frac{\ln n}{100n})^{n-1}$$
since the the degree of $v$ is $0$ in $H$ if and only if every one of the $n-1$ edges incident with $v$ is not sampled by the algorithm. So now we bound the probability that this does not happen at any vertex of the graph. Heuristically we treat the events $d_H(v) = 0$ over $v \in V$ as independent events. Then
\begin{align*}
Pr(d_H(v) \geq 1, \forall v \in V) &= \Pi_{v\in V} (1-Pr(d_H(v) = 0)) \\
&=(1-(1- \frac{\ln n}{100n})^{n-1})^n \\
&\leq e^{-n(1- \frac{\ln n}{100n})^{n-1}} &\text{using $1+x \leq e^x$} \\
\end{align*} 
So with extremely low probability $d_H(v) \geq 1$, for all $v \in V$. Hence, with high probability there exists $v \in V$ with $d_H(v) = 0$. Therefore for the cut $\delta(v)$, 
$$w(\delta_H(v)) = 0$$
while 
$$(1\pm \epsilon)\delta_G(v) = (1\pm \epsilon)(n-1)$$
so when $0 <\epsilon < 1$ and $n\geq 2$, $H$ utterly fails to be a $(1\pm \epsilon)$-cut-approximator of $G$.
\newpage
\section{}
\end{document}
